%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

%  new import
\usepackage{ragged2e}
% \usepackage{fontawesome5}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ : \justifying{#2}\par \vspace{-2pt}}
  }
}

\newcommand{\resumeDetail}[1]{
  \item[]\small{
     \justifying{#1}\par \vspace{-2pt}}
  }

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Huge Pawarit Thareechan}} & E-mail: \href{mailto:T.Pawarit@lckyn.com}{T.Pawarit@lckyn.com}\\
  Bangkok, TH & Tel: (+66)083-028-2014 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {King Mongkut's University of Technology North Bangkok(KMUTNB)}{Bangkok, TH}
            {Bachelor of Computer Engineering}{Aug. 2015 -- Apr. 2019}
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
    {Avalant CO. LTD}{Bangkok, TH}
    {Data Scientist}{Apr 2023 - present}
    \resumeItemListStart
        \resumeItem{Optimized Employee Performance}
            {
                Developed end-to-end solutions in Python to optimize employee performance and feedback processes, driving employee growth.
            }
        \resumeItem{End-to-End Data Lakehouse Project}
            {
                Led the implementation of an end-to-end data lakehouse project utilizing Apache Spark, Apache Superset, Apache Iceberg, and Min.io for efficient data storage, processing, and visualization.
            }
    \resumeItemListEnd

\resumeSubheading
    {Looloo Technology}{Bangkok, TH}
    {Machine Learning Engineer}{Aug 2021 - Mar 2023 (1 year 7 month)}
    \resumeItemListStart
        \resumeItem{Car Price Project}
        {
            Developed a regression model in Python using scikit-learn to predict car auction prices based on car brands, models, manufacturing years, and other relevant factors.
        }
        \resumeItem{Steganography}
        {
            Engineered a pipeline in Python utilizing OpenCV for image processing and manipulation, implementing steganography techniques to conceal user identification in images, audio, and backgrounds.
        }
        \resumeItem{Wav 2 Talking Head Cartoon}
        {
            Designed and implemented a neural network model using TensorFlow and Generative Adversarial Networks (GANs) to generate talking animations from spoken voices.
        }
        \resumeItem{Cardboard QR Code Classification}
        {
            Built and trained a deep learning model using TensorFlow and EfficientNet for efficient and accurate classification of QR code images.
        }
        \resumeItem{Symptom Clustering}
        {
            Developed a natural language processing (NLP) model in Python using spaCy and scikit-learn to classify symptoms from textual context, facilitating medical diagnosis.
        }
    \resumeItemListEnd

\resumeSubheading
    {iCONEXT CO., LTD.}{Bangkok, TH}
    {Software Engineer (Internship)}{Apr 2018 - Jul 2018}
    \resumeItemListStart
        \resumeItem{Line Chatbot}
        {
            Created a Line chatbot in C\# that automated the management of meeting rooms, checked availability, and facilitated reservations.
        }
        \resumeItem{Automated Sales Report}
        {
            Designed and implemented an automatic sales reporting system in C\# for weekly database updates, streamlining data analysis processes.
        }
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------Accomplishments-----------------
\section{Accomplishments}
\resumeSubHeadingListStart
\resumeSubheading
    {{Health Data Science Hackathon by BDMS }}{Bangkok, TH}
    {Reward 10,000 THB (Approximate 300 USD)}{(2021)}

\resumeSubheading
    {{Codesignal}}{Global}
    {Leaderboard top 10 - All time (Country - Thailand)}{(2020)}

\resumeSubheading
    {{Teacher's Assistant}}{Bangkok, TH}
    {Bachelor of Engineering: Computer Engineering}{(2019)}

\resumeSubheading
    {{Variable Selection using AUC optimization}}{Bangkok, TH}
    {Senior Project}{(2019)}

\resumeSubheading
    {{Cyber Security Challenge by KPMG}}{Bangkok, TH}
    {Participation}{(2018)}
\resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
    \resumeSubHeadingListStart
        \resumeSubItem{Languages}
            {
                Python, C\#, SQL, Markdown, Latex, shell, JavaScript
            }
        \resumeSubItem{Tools}
            {
                Jupyter notebook, VS Code, Apache Spark, Apache Superset, Numpy, Pandas, Regex, Git, Tensorflow, Unity(game engine)
            }
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
